### 2017-03-31 Doc/classicthesis/Chapters/Chapter01.tex
a few bib
udoc

>>>>

In recent years some new concepts have appeared in common people's vocabulary, like \textit{machine learning}, \textit{big data}, \textit{artificial intelligence}, \textit{automation}, etc., but there are two in particular that we are going to focus and try to combine: \ac{IoT} and Internet Security \& Privacy.

The \ac{IoT} is a term with a wide range of interpretations \citep{Atzori20102787}, but a breaf definition could be the set of devices, mainly resource constrained, that are interconnected between them in order to achieve a goal. This includes from lampposts with proximity sensors that talk to each other in order to light up part of the street when a passerby walks by, to a sensor on your clothes that tells the washing machine how much detergent to use.

Security \& Privacy, thanks to organizations like \href{https://wikileaks.org/}{WikiLeaks}, are now taken in consideration by any technology consumer, not only professionals. People are conscious about what their data can be used for, and demand more control over it.

And IoT has proved to not address neither security nor privacy, with recent events like the Mirai botnet DDoS attack on October 2016, considered the biggest DDoS in history \citep{jeyanthi:2017}.

\section{Motivation}

\section{Challenges}

\section{Goals}

\section{Outline of this thesis}
